A Topography of Climate Change Research

### 2017-09-28 main.tex

\subsection*{Topic Model}
\begin{itemize}
	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
    \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score. The strength of links is greater where two topics are categorised as 
\end{itemize}

@@

\subsection*{Literature Description}
\begin{itemize}
	\item Some big/interesting topics are x and y
	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
    \item
\end{itemize}

\subsection*{Information Retrieval Implications}
\begin{itemize}
    \item X keywords fit into Y topics like so...
    \item Finding similar documents, how does this work with topics as opposed to keywords?
    \item Similar documents more or less likely to be across disciplinary boundaries ??
\end{itemize}

\section*{Conclusion}
\begin{itemize}
	\item A very simple topic model provides an overview of the whole landscape.
    \item This allows researchers / assessment makers to identify areas that have grown recently
    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
    \item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
\end{itemize}

@@

\begin{itemize}
\item Model selection: NMF \citep{Lee1999}
\item How does it work? Advantages: Simple, scalable: better results than with other solutions, if only because it was possible to iterate with large document collections. LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
\item Topic model browser \citet{Chaney2012}
\item Human Validation: 
\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
\item Which topics get the most citations?

>>>>

\subsection*{Topic Model}
\begin{itemize}
	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
    \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score. The strength of links is greater where two topics are categorised as being in the same working group. This relationship is statistically significant (see SI)
\end{itemize}

@@

\begin{itemize}
	\item Some big/interesting topics are x and y
	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
    \item
\end{itemize}

%\subsection*{Information Retrieval Implications}
%\begin{itemize}
%    \item X keywords fit into Y topics like so...
%    \item Finding similar documents, how does this work with topics as opposed to keywords?
%    \item Similar documents more or less likely to be across disciplinary boundaries ??
%\end{itemize}

\section*{Conclusion}
\begin{itemize}
	\item A very simple topic model provides an overview of the whole landscape.
    \item This allows researchers / assessment makers to identify areas that have grown recently
    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
	\item AR5 seemed to have less comprehensive coverage of x topics. This was a particular issue in WG y.
	\item This may not be an issue, there could be good reasons for this, but these should be made transparent.
	\item For the next assessment report, x topics may require particular attention.
	\item The emerging topic on CCS resonates with a growing recognition of the importance of negative emissions and the lack of understanding about how they could fill their role. This will be of particular importance for the IPCC special report on 1.5 degrees.
    %\item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
\end{itemize}

@@

\begin{itemize}
\item Topic modelling in general: reducing large matrix of documents to words to two smaller matrices of topics x words and topics x documents.
\item Model selection: NMF \citep{Lee1999}
\item How does it work? Advantages: Simple, scalable: better results than with other solutions%, if only because it was possible to iterate with large document collections. LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
\item Topic model browser \citet{Chaney2012}
\item Merging with IPCC citation dataset - caveats...
\item Network explanation
\item Regression of network score on dummy variable for same
%\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
%\item Which topics get the most citations?

### 2017-09-28 pres/proposal.tex

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}

@@

@@

\title[Short Title]{Title}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{\includegraphics[height=1cm,width=2cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}}

@@

\addtobeamertemplate{frametitle}{}{%
	\begin{tikzpicture}[remember picture,overlay]
	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}};
	\end{tikzpicture}}

\begin{frame}{Frame Title}

@@

\begin{frame}{Frame Title}
	\small
	\bibliography{/home/max/Documents/library/bibliography}
\end{frame}

>>>>

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}

@@

\definecolor{rd}{HTML}{2F2A40}
\definecolor{methods}{HTML}{C6C6C6}
\definecolor{research}{HTML}{8F84BE}
\definecolor{skills}{HTML}{7A7A7A}
\definecolor{rc}{HTML}{AC152A}

@@

\title[Climate Topography]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
	\,
	\includegraphics[height=1cm]{hertie_logo.png}
}

@@

\addtobeamertemplate{frametitle}{}{%
	\begin{tikzpicture}[remember picture,overlay]
	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{MCC_Logo_RZ_rgb.jpg}};
	\end{tikzpicture}}

\begin{frame}{Context}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item Climate Change is complicated
			\item The IPCC \textit{assess} the science on climate change
			\item These assessments should be comprehensive, credible and relevant
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

@@

\begin{frame}{Motivation}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
\begin{figure}
	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
	\caption{Source: \citet{Minx2017} }
\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Comprehensive, credible and relevant assessments become
				more challenging as the literature grows
			\end{itemize}
		\begin{remark}[]
			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
		\end{remark}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Approach - Words, words, words}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{volume_variety_bible.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Topic modelling is a way of reducing the dimensionality of a corpus of documents
				\item A large matrix of documents x words is factorised by
				a matrix of topics x words and a matrix of topics x documents
			\citep{Lee1999}
				\item Topics describe the latent structure of the document corpus

			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - explanation}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/biomass_eg.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Documents are mixtures of topics, based on the words which occur in them
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - structure}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/network_wg_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - growth}

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/hot_topics_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item Negative emissions related topics have shown strong growth in recent years
				\item As have topics on food security and cities
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - gaps in coverage}

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item ``Niche'' topics on specific technological solutions, are less well covered
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Next steps}

\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
%		\end{center}
%	\end{column}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\begin{itemize}
				\item Can I get a clearer research question, and make the analysis less descriptive?
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Outlook}

\begin{figure}

\tiny

\begin{ganttchart}[
	y unit title=0.3cm,
	y unit chart=0.5cm,
	x unit= 0.2cm,
	vgrid,hgrid,
	vgrid={{dotted,dotted,black}},
	title height=1,
	%     title/.style={fill=none},
	title label font=\bfseries\scriptsize,
	%bar/.style={fill=blue},
	bar height=0.7,
	bar label font=\tiny,
	%   progress label text={},
	group right shift=0,
	group top shift=0.7,
	group height=.3,
	group peaks width={0.2},
	inline]{1}{42}
	\gantttitle{2017}{9}
	\gantttitle{2018}{12}
	\gantttitle{2019}{12}
	\gantttitle{2020}{9} \\
	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\

	% HERTIE
	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\

	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\

	% HERTIE
	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\

	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\

	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline

\end{ganttchart}

\end{figure}

\begin{frame}{Frame Title}
	\small
	\bibliography{C:/Users/galm/Documents/library/library}
\end{frame}
